Object-Oriented Internet\\ Cloud Interoperability

### 2021-01-07 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final review of the latex text #37
- working copy

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855}. In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, any human interaction must be recognized as impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.

>>>>

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855, 10.1007/978-3-030-50426-7_22}. In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, any human interaction must be recognized as impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.
